\section{Background}
\label{bg}

%Background...
%
%Typical length: 0 pages to 1.0.
%
%Background and Related Work can be similar.  Most citations will be
%in this section.
%
%1. Describe past work and criticize it, fairly.  Use citations to
%JUSTIFY your criticism!  Problem: hard to compare to YOUR work, b/c
%you've not yet described your work in enough detail.  Solution: move
%this text to Related Work at end of paper.
%
%2. Describe in some detail, background material necessary to
%understand the rest of the paper.  Doesn't happen often, esp. if
%you've covered it in Intro.
%
%Example, submit a paper to a storage conference: reviewers are
%experts in storage.  Don't need to tell them about basic disk
%operation.  But if your paper, say, is an improvement over an
%already-advanced data structure (eg., COLA), then it'd make sense to
%describe basic COLA algorithms in some detail.
%
%Important: open the bg section with some "intro" text to tell reader
%what to expect (so experienced readers can skip it).
%
%If your bg material is too short, can fold it into opening of
%'design' section.


BFS is an algorithm for traversing or searching tree or graph data
structure. The algorithm finds shortest paths from a given source node
to all other nodes, in terms of the number of edges in the path. It
starts at the source node and explores the neighbour nodes first
before moving to the next level neighbours.  Its a well known research
topic. A variety of parallel BFS algorithms trying to improve
complexity, parallelism, distributed cache and io performance have
been proposed till date.
\newline
%Some of these parallel algorithms are \emph{work efficient}, meaning
%that the total number of operations performed is the same to within a
%constant factor as that of a comparable serial algorithm.
A recent paper proposed Hybrid++ BFS algorithm for an accelerated
processing unit (APU), a heterogeneous processor which fuses the CPU
and GPU cores on a single die~\cite{HYBRIS}. Hybrid++ leverages the
strength of CPUs and GPUs for serial and data-parallel execution,
respectively, to carefully partition BFS by selecting the appropriate
execution-core and graph-traversal direction for every search
iteration.
\newline
\emph{NUMA-optimized Parallel Breadth-first Search on Multi-core
Single-node System}~\cite{NUMA-BFS} proposed a non-uniform memory
access (NUMA)-optimized BFS, that reduced memory accesses to remote
RAM on a NUMA architecture system.
\newline
\emph{Performance evaluation of breadth-first search on Intel Xeon
Phi} [7], evaluates BFS performance evaluation on a recently released
high-performance Intel Xeon Phi coprocessor. They examine the
previously proposed Queue-based and Read-based approaches to BFS
implementation. They also apply several optimization techniques, such
as manual loop unrolling and prefetching, that significantly improve
performance on Intel Xeon Phi. On a representative graph set, Intel
Xeon Phi 7120P demonstrates 78\% maximum and 37\% average speedup as
compared to the Intel Xeon E5-2660 processor.
\newline
Though the research on parallel BFS has
been extensive, very few of these focus on energy efficieny.
\newline
Current cluster implementations suffer from high latency data
communication with large volumes of transfers across nodes, leading to
inefficiency in performance and energy consumption. \emph{Large Scale
Energy- Efficient GraphTraversal: A Path to Efficient Data-Intensive
Supercomputing}~\cite{INTEL-BFS} tried to overcome these constraints
using a combination of efficient low- overhead data compression
techniques to reduce transfer volumes along with latency-hiding
techniques.
\newline
\emph{Fast and Energy-efficient Breadth-First Search on a Single NUMA
System}~\cite{ENERGY-BFS} investigated the computational complexity of
the bottom-up, a major bottleneck in NUMA-optimized BFS.
\newline
Considering the recent trends in application of graph algorithms in
big data and information analysis, energy efficiency is a major
concern. In this project we have explored some of the existing
parallel BFS algorithms in terms of energy efficiency and tried to
develop useful insights based on the results.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:
