\section{Conclusions}
\label{conc}

%Conclusion text...
%
%Length: 0.25-0.5 pages max (1-2 pgfs)
%
%Summary of key contributions (should match your design goals).
%Not summary of whole paper.  Any novel contributions mentioned.
%Summarize good eval results.
%
%Key: give reader the "take home" message.

We have introduced a UID based authentication mechanism inside
eCryptfs.  It is an additional check to prevent unauthorized users
inside a trusted host environment from accessing the encrypted data,
even root user is not allowed.  Based on our results we see that this
mechanism works for all type of users irrespective of their privilege
level and does not add much overhead in the performance of eCryptfs.
This policy based access control can be extended to other parameters
like process id, tty, application.

\paragraph{Future Work}
We plan to integrate role based access control (RBAC) with flexible
number of admin and users using the system.  We will extend the access
policies employing restrictions based on pid, sid, process name, etc.
To address the problem of non-persistent super block, we plan to add a
policy file for eCryptfs to make the \emph{ecryptfs\_allowed\_list}
persistent across reboot/remounts.  As of now Linux kernel keyring
supports key expiration, but eCryptfs does not.  We plan to add the
key expiration support to eCryptfs.

%Future work text...
%
%Typical length: 0.25-0.33 pages max
%
%Don't write too much:
%- the more you write, the more work appears "premature"
%- takes up important space (small impact on acceptance)
%
%Often folded as subsection of conclusions.
%
%Describe most important 1-3 "novel/research" future work ideas.
%
%Avoid "short term" future goals.  Focus on long-term goals, well
%beyond the scope of THIS paper.  Avoid stuff that might be
%considered as should have been part of this work.
%
%Give reader some ideas of HOW you plan to go about investigating
%future ideas.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:
